An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-04 docs/icccn2009/paper.tex
Add more material
git-svn-id: svn://localhost/netbeams/trunk@330 559edde2-a4d4-44e0-96fc-4035e40d7396

\author{\authorblockN{XXX}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: XXX@sfsu.edu}}

@@

@@

\section{Requirement Analysis}

@@

@@

@@

\begin{figure*}
\centering
\epsfig{file=netbeams, width=10cm}
\caption{\label{FIG_NETBEAMS} NetBEAMS architecture.}
\end{figure*}

@@

Cellular communication platform.

@@

@@

%\bibliography{../literature/lit}
%\bibliographystyle{plain}

>>>>

\author{\authorblockN{A. Puder, T. Johnson, K. Sales, M. Sales}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: \{arno$\mid$tlj$\mid$klebers$\mid$msales\}@sfsu.edu}
\and
\authorblockN{D. Robinson}
\authorblockA{San Francisco State University \\
Romberg Tiburon Center \\
3150 Paradise Drive \\
Tiburon, CA 94920 \\
EMail: dhr@sfsu.edu}}

@@

\cite{roemer:2004}

@@

\section{Background}

@@

---

The YSI 6600EDS V2 Sonde is a water quality monitoring device that
gathers water quality data, and operates in fresh, sea, or
polluted water. It is under 22 inches (under 55 cm) in length, 3.5
inches (8.9 cm) in diameter, and weighs approximately 7 pounds (3.18
kg). It operates at temperatures between -5 to +50 deg C and at depths
up to 656 feet (200 meters).  It uses 8 C-size Alkaline Batteries or
External 12 VDC. Battery life can last up to 75 days depending on
sensor configuration. The Sonde's bulkhead contains multiple pin
connectors to support sensor probes for measuring the following:

\begin{table}[h]
\caption{\label{TAB_SONDE_MEASUREMENTS} YSI Sonde measurements.}
\centering
\begin{tabular}{|l||l|}
\hline
\multicolumn{1}{|c||}{\textbf{Name}} &
\multicolumn{1}{c|}{\textbf{Description}} \\ \hline \hline
\texttt{Date}    & Year/Month/Day. \\ \hline
\texttt{Time}    & Hour:Minute:Second. \\ \hline
\texttt{Temp}    & Temperature in degrees Celcius. \\ \hline
\texttt{SpCond}  & Specific Description in microSiemens
                   per centimeter. \\ \hline
\texttt{Cond}    & Conductivity in microSiemens per centimeter. \\ \hline
\texttt{Resist}  & Resistivity in Ohms $*$ centimeter. \\ \hline
\texttt{Sal}     & Salinity in parts per thousand. \\ \hline
\texttt{Press}   & Pressure in pounds per square inch relative. \\ \hline
\texttt{Depth}   & Water column in meters. \\ \hline
\texttt{pH}      & pH in standard units. \\ \hline
\texttt{phmV}    & millivolts associated with the pH reading. \\ \hline
\texttt{ODOSat}  & Dissolved oxygen in \% air saturation. \\ \hline
\texttt{ODOConc} & Dissolved oxygen in mg/L. \\ \hline
\texttt{Turbid}  & Turbidity in nephelometric turbidity units. \\ \hline
\texttt{Battery} & Total Volts remaining in batteries.  \\ \hline
\end{tabular}
\end{table}

Dissolved oxygen
Conductivity/Temperature
Fouling Resistant pH/ORP
Chloride
Ammonium
Nitrate
Turbidity
Chlorophyll
Rhodamine
PC-Blue-green Algae
PE-Blue-gren Algae

Each probe may have multiple sensors.  A computer can interface with
the Sonde via RS-232C or SDI-12. The Sonde can be configured to
collect data samples in discrete or unnattended mode.  Discrete mode
is normally performed while a technician manages the Sonde during the
sampling process. In this mode the Sonde is usually connected via 650
MDS Display/Logger or a serial cable connected to a PC.  The sampling
frequency is usually set to a high frequency in this mode.  Unattended
mode is performed usually when the Sonde is deployed offshore or in a
remote body of water.  The sampling frequency is usually set for a
longer period of time (i.e. 5 - 15 min). The Sonde is configured via a
set of menus that can be accessed through a terminal session over
RS232. Through these menus, the Sonde can be configured to start
logging data to an internal file.  To view the data as it's being
captured, the option to show live data is chosen and the data can then
seen via a serial terminal session at each interval.

---

@@

\begin{code}
<xs:schema ...>
  <xs:complexType name="DSPMessage">
    <xs:element name="Header" type="Header"/>
  </xs:complexType>

  <xs:complexType name="Header">
    <xs:sequence>
      <xs:attribute name="messageID"/>
      <xs:attribute name="originatingDP"/>
      <!-- ... -->
    </xs:sequence>
  </xs:complexType>
</xs:schema>
\end{code}

@@

\begin{figure*}
\centering
\epsfig{file=netbeams, width=14cm}
\caption{\label{FIG_NETBEAMS} NetBEAMS architecture.}
\end{figure*}

@@

The Huawei E220 is a USB modem that supports HSDPA, UMTS, EDGE packet
data services at maximum transmission rates of 3.6Mbps, 384kbps, and
236.8kbps respectively. HSDPA and UMTS operate at 2100MHz while GSM,
GPRS, and EDGE operate at 900, 1800, and 1900MHz. The modem connects
to the Verdex Pro XM4 motherboard via a mini USB interface (supporting
USB 2.0). Linux kernels since 2.6.20 include support for E220 drivers.
This includes the linux kernel on the gumstix which runs 2.6.21.  The
gumstix communicates with the modem using the PPP protocol and
accesses the cellular network using a data plan from AT\&T.

@@

\begin{code}
<xs:schema ...>
<xs:import schemaLocation="dsp-message.xsd"/>

<xs:element name="SondeDataMessage">
  <xs:complexType>
    <xs:complexContent>
      <xs:extension base="DSPMessage">
        <xs:sequence maxOccurs="unbounded"
                     minOccurs="1">
          <xs:element name="sondeData"
                      type="sondeDataType"/>
        </xs:sequence>
      </xs:extension>
    </xs:complexContent>
  </xs:complexType>
</xs:element>

<xs:complexType name="sondeDataType">
  <xs:sequence>
    <xs:element name="Date" type="xs:date"/>
    <xs:element name="Time" type="xs:time"/>
    <xs:element name="Temp" type="xs:float"/>
    <xs:element name="SpCond" type="xs:float"/>
    <!-- ... -->
  </xs:sequence>
</xs:complexType>
</xs:schema>
\end{code}

@@

\bibliography{lit}
\bibliographystyle{plain}
